Title: A proof-of-concept study

### 2022-01-08 paper.tex
update

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
    \caption{
             Comparison between the case with a clumpy (first column from left)\
             and a smooth disk (second) in a stratified atmosphere\
             shows that the density distribution of the dense disk has insignificant effect\
             on the overall dynamics of the bubbles. However, the bubbles with the smooth disk (third)\
             in an uniform atmosphere is spherical-shape,\
             suggesting the stratification facilitate bubbles elongation.\
             The rightmost column shows that the bubbles without disk is tilted even\
             in the stratified atmosphere, indicating dense disk is a crucial component\
             for axis-symmetric bubbles formation.\
             In all cases, bipolar jets are injected at the origin along $z=-y$ direction\
             for a duration of 1.2 Myr.
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through jet sources show that the under pressure, cold, and dense bubbles (dashed box)\
             only appear if disk is present.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

>>>>

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
    \caption{
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through a bipolar jet sources injecting along $z=-y$ direction from\
             the origin for a duration of 1.2 Myr under four different circumstances from left column to right.\
             Comparison between the cases with a clumpy (first column from left)\
             and with a smooth disk (second) in a stratified atmosphere\
             shows that the density distribution of the dense disk has insignificant effect\
             on the overall dynamics of the bubbles. However, the outer bubbles with the smooth disk (third)\
             in an uniform atmosphere is spherical-shape,\
             suggesting the stratification facilitates the outer bubbles elongation significantly.\
             Also, the first three and the rightmost columns show that the most inner bubbles (dashed box)\
             can only appear with the disk, and without the disk, the outer bubbles will be tilted,
             indicating the dense disk is a crucial component for\
             the formation of the axis-symmetrically outer bubbles and of the most inner bubbles.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
  \end{figure}
